\section{Scenarios}\label{sec:scenarios}

Amusement parks surely represent a popular form of entertainment for people of all ages and with different interests.
This is one of the reasons why, specially during holiday times, these parks attract a considerable amount of visitors and tend to be significantly crowded.
Although this is greatly profitable for the parks themselves, unfortunately it is not the ideal situation for the visitors as chances are that they will have to spend most of their time waiting in a queue.
This situation becomes even more unattractive for large groups of visitors, such as families with children, or under unpleasant weather conditions, such as rain or summer heat.
In order to improve the overall visitors' experience, the \textbf{situated recommendation system} could suggest the most suitable attractions for them.

In addiction, such system could be also convenient for amusement parks' managers.
In fact, visitors would be more attracted to the parks providing such facilities, meaning that the attendance of visitors would increase.
Also, it is important mentioning that not all attractions inside the parks are rides or roller coasters.
In fact, parks can also contain restaurants or shops.
A situated recommendation regarding these kinds of attraction may involve marketing strategies that would make visitors willing to go there.
Given all the advantages that a service like that could provide to the visitors, managers could also decide to supply it as an additional ``premium" service.